Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2023-08-15 writing/CONUS_AOD.qmd
Moved around some sections of `CONUS_AOD.qmd`.
Put time differences in text instead of tables.

After collocation there were \## matched AOD retrievals from \## AERONET sites in CONUS. The median absolute difference from the labeled overpass time (one per 1200-km wide tile) and the time of the matched AERONET observation was \## minutes (25^th^ and 75^th^ percentiles of \## and \## minutes, respectively). While the distribution of AOD is skewed, our estimate of retrieval error and the dependent variable for our predictive model, *diff~AOD~*, was fairly symmetric and Gaussian.

@@

### Performance by year

```{r strata_year}
kbl(pretty.table.numbers(tar_read(cv.summary)[-1, .SD, .SDcols = -patterns("Q[1-9]")]),
    align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(1:13, width = "1.1cm")
```

```{r strata_month}
result <- dt[,
    keyby = .(Month = month(lubridate::as_datetime(time.sat))),
    eval(performance.j)]
result[, Month := month.abb[Month]]
kbl(pretty.table.numbers(result[, .SD, .SDcols = -patterns("Time")]), align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(1:13, width = "1.1cm")
```

@@

```{r strata_noaa_regions, fig.pos="H"}
# performance by NOAA climate regions
by.region = dt[, eval(performance.j), keyby = state.noaa.region]
kbl(pretty.table.numbers(by.region[, .SD, .SDcols = -patterns("Time")]),
    align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(2:13, width = "1.1cm")
```

@@

@@

```{r strata_high_aod, fig.pos="H"}
by.highaod = dt[, eval(performance.j), by = .(aod_high = y.ground > 0.6)]
kbl(pretty.table.numbers(by.highaod[, .SD, .SDcols = -patterns("Time")]),
    align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(2:13, width = "1.1cm")
```

### Performance by number of overpasses in collocation that site-day

```{r strata_overpasses, fig.pos="H"}
dt[, overpasses := .N, by = .(site, lubridate::as_date(time.ground))]
by.overpasses = dt[, eval(performance.j), keyby = overpasses]
kbl(pretty.table.numbers(by.overpasses[, .SD, .SDcols = -patterns("Time")]),
    align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(2:13, width = "1.1cm")
```

@@

```{r strata_qa}
by.qabest = dt[, eval(performance.j), by = qa_best]
kbl(pretty.table.numbers(by.qabest[, .SD, .SDcols = -patterns("Time")]),
    align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(1:13, width = "1.1cm")
```

@@

>>>>

After collocation there were \## matched AOD retrievals from \## AERONET sites in CONUS. The median absolute difference from the labeled overpass time (one per 1200-km wide tile) and the time of the matched AERONET observation was `r tqs = round(quantile(dt[, abs(as.numeric(difftime(units = "secs", time.sat, time.ground)))], c(.25, .5, .75))); tqs["50%"]` s (25^th^ and 75^th^ percentiles of `r tqs["25%"]` and `r tqs["75%"]` s, respectively). While the distribution of AOD is skewed, our estimate of retrieval error and the dependent variable for our predictive model, *diff~AOD~*, was fairly symmetric and Gaussian.

@@

@@

```{r strata_noaa_regions, fig.pos="H"}
# performance by NOAA climate regions
by.region = dt[, eval(performance.j), keyby = state.noaa.region]
kbl(pretty.table.numbers(by.region),
    align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(2:13, width = "1.1cm")
```

@@

```{r strata_month}
result <- dt[,
    keyby = .(Month = month(lubridate::as_datetime(time.sat))),
    eval(performance.j)]
result[, Month := month.abb[Month]]
kbl(pretty.table.numbers(result), align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(1:13, width = "1.1cm")
```

@@

```{r strata_high_aod, fig.pos="H"}
by.highaod = dt[, eval(performance.j), by = .(aod_high = y.ground > 0.6)]
kbl(pretty.table.numbers(by.highaod),
    align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(2:13, width = "1.1cm")
```

@@

```{r strata_qa}
by.qabest = dt[, eval(performance.j), by = qa_best]
kbl(pretty.table.numbers(by.qabest),
    align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(1:13, width = "1.1cm")
```

@@

## Performance by year

```{r strata_year}
kbl(pretty.table.numbers(tar_read(cv.summary)[-1]),
    align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(1:13, width = "1.1cm")
```

## Performance by number of overpasses in collocation that site-day

```{r strata_overpasses, fig.pos="H"}
dt[, overpasses := .N, by = .(site, lubridate::as_date(time.ground))]
by.overpasses = dt[, eval(performance.j), keyby = overpasses]
kbl(pretty.table.numbers(by.overpasses),
    align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(2:13, width = "1.1cm")
```
